---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(dplyr)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sumr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of sumr is to provide a workaround for the currently very noisy `dplyr::summarise()`:

```{r}
library(dplyr)
summarised <- starwars %>%
  group_by(species) %>%
  summarise(mass = mean(mass))
```

You can silence this message using `options(dplyr.summarise.inform = FALSE)`. If you'd rather not write this at the top of every script, you can use this package to make the grouping of your result explicit with roughly the same number of characters:

```{r}
library(sumr)

# drops grouping
starwars %>%
  group_by(species) %>%
  sumr(mass = mean(mass))

# peels back one layer of grouping per call
starwars %>%
  group_by(gender, species) %>%
  sumr_peel(mass = mean(mass, na.rm = TRUE)) %>%
  sumr_peel(mass = mean(mass, na.rm = TRUE))

# keeps current grouping
starwars %>%
  group_by(species) %>%
  sumr_keep(mass = mean(mass))
```

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("paleolimbot/sumr")
```
