---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(dplyr)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sumr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of sumr is to provide a workaround for the noisy and permissive `dplyr::summarise()`. It's seriously awesome and powerful! But you can get burned if you did not expect this behaviour.

```{r}
library(dplyr)
starwars %>%
  group_by(species) %>%
  summarise(mass = mean(mass)) %>% 
  count(species)

starwars %>%
  group_by(species) %>% 
  summarise(films = unique(unlist(films))) %>% 
  count(species)
```

You can silence this message using `options(dplyr.summarise.inform = FALSE)`. If you'd rather not write this at the top of every script, you can use this package to make the grouping of your result explicit with roughly the same number of characters:

```{r}
library(sumr)

# drops grouping
starwars %>%
  group_by(species) %>%
  sumr(mass = mean(mass))

# peels back one layer of grouping per call
starwars %>%
  group_by(gender, species) %>%
  sumr_peel(mass = mean(mass, na.rm = TRUE)) %>%
  sumr_peel(mass = mean(mass, na.rm = TRUE))

# keeps current grouping
starwars %>%
  group_by(species) %>%
  sumr_keep(mass = mean(mass))
```

`sumr()` checks for length-one results, but you can use `retbl()` to use the awesome new features of `summarise()`. Because `retbl()` typically computes a new data frame for each group, groups are kept:

```{r}
starwars %>%
  group_by(species) %>% 
  retbl(films = unique(unlist(films)))
```

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("paleolimbot/sumr")
```
